---
title:    "Wine Quality Prediction Model"
subtitle: "Exploritory Analysis and Prediction of Wine Quality <br />based on three predictors"
author:   "Greig Robertson"
date:     "12/04/2017"
output:
  ioslides_presentation:
    widescreen: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Common libraries and variables

library(tidyverse)
library(caret)
library(randomForest)
library(knitr)
library(kableExtra)

data_dir <- "../app/data/"
```

<style>
body {
    background-color: #6d9eed;
}
.textmed {
  font-size: 14pt;
}
.textsmall {
  font-size: 12pt;
}
.table td {
  font-size: 10pt;
}
</style>

## Summary


<div class="textmed">

This data product uses available data sets for red and white Portuguese wine.  The data was analysed and a model (random forest) was created to predict the quality of wine based on the results of physicochemical tests.

A Shiny application was developed based on these results using a simpler (faster) linear regression model.

</div>

<div class="textsmall">

- Wine quality data is available from [Kaggle](https://www.kaggle.com/uciml/red-wine-quality-cortez-et-al-2009)
- More details are available at [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/wine+quality)
- Citation is available [here](https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality.names)

</div>


## Data Processing

```{r data_process, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
col_spec <- cols(
  `fixed acidity`        = col_double(),
  `volatile acidity`     = col_double(),
  `citric acid`          = col_double(),
  `residual sugar`       = col_number(),
  chlorides              = col_double(),
  `free sulfur dioxide`  = col_number(),
  `total sulfur dioxide` = col_double(),
  density                = col_double(),
  pH                     = col_number(),
  sulphates              = col_double(),
  alcohol                = col_number(),
  quality                = col_integer()
)

read_wq_csv <- function(wine_colour) {
  filename      <- paste0(data_dir, "winequality-", wine_colour, ".csv")
  w_data        <- read_delim(filename, col_types=col_spec, delim=';')
  w_data$colour <- wine_colour
  w_data
}

white_wine_data  <- read_wq_csv("white")
red_wine_data    <- read_wq_csv("red")

wine_data        <- rbind(red_wine_data, white_wine_data)
names(wine_data) <- make.names(names(wine_data))
wine_data$colour <- as.integer(wine_data$colour == "red")


```

<div class="textsmall">

- The data were loaded from two semi-colon delimited files (one file for red, one for white)
- The data sets were combined `rbind()` and an extra column indicating color was added

The available columns are:

</div>

```{r echo=FALSE, message=FALSE, warning=FALSE}
names(wine_data) %>% kable("html") %>% kable_styling()
```

<br />

<div class="textsmall">

Where quality is on a scale of 0 (bad) to 10 (very good).

</div>


## Model - random forest

<div class="textsmall">

A random forest model was trained and tested against a data set, further partitioned into training and testing data sets.  The overall results from the confusion matrix are:

</div>


<pre class="textsmall">

```{r model, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
inTrain      <- createDataPartition(y = wine_data$quality, p = 0.75, list = FALSE)
tab_training <- wine_data[inTrain,]
tab_testing  <- wine_data[-inTrain,]

tab_model_rf <- randomForest(quality ~ ., data = as.data.frame(tab_training), importance = TRUE) # 0.664
tab_predict  <- predict(tab_model_rf, newdata = tab_testing[,-12])
cfm          <- confusionMatrix(round(tab_predict), tab_testing$quality)

cfm$overall %>% kable("html") %>% kable_styling()
```
</pre>


<div class="textsmall">

The accuracy is quite low.

</div>


## Model - linear regression

<div class="textsmall">

This model was created to:

- Create a model to predict quality of wine based on the other variables
- Determine the *three* main predictors of quality for use in a smaller model (using `varImp()`)

A smaller model using linear regression was used since this was much faster than the random forest model.
For a user interactive data product, model accuracy was traded off against performance.

</div>


```{r model_results, echo=FALSE, message=FALSE, warning=FALSE}
varimp_temp <- varImp(tab_model_rf)
tibble(name = rownames(varimp_temp), value = varimp_temp$Overall ) %>%
  arrange(desc(value)) %>%
  kable("html", col.names = c("Name", "Value")) %>% kable_styling()
```

## Shiny Application Details

The application is available [here](https://greigar.shinyapps.io/ddp-wine-quality/). There are three tabbed plots on the Shiny site showing

- Square points for each observation
- A linear regression line through the markers for each predictor
- A circular point showing the predicted quality

You can:

- Set the levels for alcohol, free sulfur dioxide and volatile acidity
- Animate the alcohol level by pressing the play triangle

<div class="textsmall">

Git repo: https://github.com/greigar/ddp-wine-quality

</div>


## Future Development

Ideas for extending this data product are:

- Include data from other wine reviews to improve the accuracy
- Improve the model (perhaps only use random forest)


