---
title:    "Wine Quality Prediction Model"
subtitle: "Predict Wine Quality based on three predictors"
author:   "Greig Robertson"
date:     "12/04/2017"
output:   ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary of Objective

Wine quality data is available from https://www.kaggle.com/uciml/red-wine-quality-cortez-et-al-2009.  More details are available at UCI Machine Learning Repository - https://archive.ics.uci.edu/ml/datasets/wine+quality

Citation from https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality.names

  This dataset is public available for research. The details are described in [Cortez et al., 2009].
  Please include this citation if you plan to use this database:

  P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis.
  Modeling wine preferences by data mining from physicochemical properties.
  In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

  Available at: [@Elsevier] http://dx.doi.org/10.1016/j.dss.2009.05.016
                [Pre-press (pdf)] http://www3.dsi.uminho.pt/pcortez/winequality09.pdf
                [bib] http://www3.dsi.uminho.pt/pcortez/dss09.bib



## Data Processing

```{r plotly, echo=FALSE, message=FALSE, warning=FALSE}
```

## Model

```{r plotly, echo=FALSE, message=FALSE, warning=FALSE}
```

## Shiny Application Details

There are three tabbed plots on the Shiny site showing.... A linear regression line is fitted through the markers for each predictor...

You can:

- Set the levels for alcohol, free sulfur dioxide and volatile acidity
- Animate the alcohol level by pressing the play triangle

## Future Development

