---
title:    "Wine Quality Prediction Model"
subtitle: "Predict Wine Quality based on three predictors"
author:   "Greig Robertson"
date:     "12/04/2017"
output:   ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary of Objective

<font size="4">

</font>

<font size="3">
- Wine quality data is available from [Kaggle](https://www.kaggle.com/uciml/red-wine-quality-cortez-et-al-2009)
- More details are available at [UCI Machine Learning Repository](https://archive.ics.uci.edu/ml/datasets/wine+quality)
- Citation is available [here](https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality.names)
</font>


## Data Processing

```{r plotly, echo=FALSE, message=FALSE, warning=FALSE}
```

## Model

```{r plotly, echo=FALSE, message=FALSE, warning=FALSE}
```

## Shiny Application Details

There are three tabbed plots on the Shiny site showing.... A linear regression line is fitted through the markers for each predictor...

You can:

- Set the levels for alcohol, free sulfur dioxide and volatile acidity
- Animate the alcohol level by pressing the play triangle

## Future Development

